% Elegant Notebook Template
% A professional LaTeX template with customisable settings for academic and research work

\documentclass[a4paper,11pt]{report}

% Load theme switching functionality
\input{config/theme}

% Select your theme - first parameter is font theme, second is colour theme
% Font themes: modern, classic, elegant, academic, scientific, professional, contemporary
% Colour themes: cambridge-blue, cambridge-classic, cambridge-forest, cambridge-sunset, cambridge-river,
%              oxford-blue, oxford-mist, oxford-monochrome, summer-skies, aurora-skies, 
%              twilight-skies, midnight-skies, vintage-rose, emerald, royal-purple, arctic, autumn
\usetheme{modern}{cambridge-blue}

% Load the Elegant Notebook settings
% The font theme is set by the \usetheme command above
\input{config/settings}

% Starting the document
\begin{document}

% Generate the title page
\input{config/title-page}

% Adding a table of contents
\tableofcontents
\newpage

% Chapter 1: Introduction
\chapter{Welcome to Your Elegant Notebook}
Welcome to the Elegant Notebook template! We have designed this template to help you create stunning and professional documents with ease. Whether you are taking notes, writing a research paper, or compiling a report, our goal is to make your work shine.

This template is built on a foundation of consistent styling, thoughtful typography, and a powerful theming system.

\begin{notetbox}[Key Features at a Glance]
Here is a glimpse of what you can do:
\begin{itemize}
    \item Craft a unique look with our one-step \textbf{font and colour theme switcher}.
    \item Organise your thoughts with beautifully designed \textbf{custom boxes} for notes and examples.
    \item Showcase your work with elegant support for \textbf{mathematics}, \textbf{code listings}, and \textbf{bibliographies}.
    \item Focus on your content, knowing the design is polished and professional.
\end{itemize}
\end{notetbox}

Let's get started and bring your ideas to life!

% Chapter 2: Getting Started
\chapter{Getting Started in Three Simple Steps}
Getting started is straightforward. Just follow these three steps:

\begin{enumerate}
    \item \textbf{Personalise Your Document}: Open \inlinecode{config/metadata.tex} and add your title, author, and other details.
    \item \textbf{Choose Your Style}: In this file (\inlinecode{elegant-notebook.tex}), find the \inlinecode{\\usetheme} command. Pick your favourite font and colour theme to match your taste. See Chapter \ref{chap:theming} for a full list of themes!
    \item \textbf{Compile Your Notebook}: Run one of the provided scripts to compile your document.
\end{enumerate}

\section{Compiling Your Document}
\label{sec:compilation}
For a quick preview without bibliography processing, use:
\begin{lstlisting}[language=bash]
./simple-compile.sh
\end{lstlisting}

For a full compilation with bibliography support (this requires the \inlinecode{biber} engine), run:
\begin{lstlisting}[language=bash]
./compile.sh
\end{lstlisting}

And that's it! You are ready to start writing.

% Chapter 3: Showcase of Core Features
\chapter{Showcase of Core Features}
\label{chap:features}
This template includes a rich set of features to make your content look its best. Let's explore some of them.

\section{Effortless Typography and Text}
The template provides clean, readable typography right out of the box. You can easily format your text:

\begin{itemize}
    \item Normal text is optimised for readability.
    \item \textbf{Bold text} for giving emphasis.
    \item \textit{Italic text} is perfect for definitions or foreign terms.
    \item \texttt{Monospace text} for technical terms.
    \item \textsf{Sans-serif text} for headings and UI elements.
    \item Of course, you can use \textcolor{accentcolor}{coloured text} and \textcolor{highlightcolor}{highlighted text}, too!
\end{itemize}

Hyperlinks, like this one to the \href{https://www.latex-project.org/}{LaTeX Project}, are styled to fit seamlessly.

\section{Engaging Custom Boxes}
Highlight key information and provide clear examples with our custom box environments.

\subsection{Note Boxes}
Use a `notetbox` to draw attention to important points, warnings, or helpful tips.

\begin{notetbox}
    This is a note box. It is perfect for highlighting information that your reader should not miss.
    
    Note boxes support multiple paragraphs and are styled using your theme's main colour.
\end{notetbox}

\subsection{Example Boxes}
The `exampletbox` is designed to showcase examples, from mathematical proofs to code snippets.

\begin{exampletbox}
    This is an example box, styled with your theme's accent colour.
    
    You can include anything you like, such as a famous equation: $E = mc^2$.
\end{exampletbox}

\section{Beautiful Code Listings}
Whether you are writing a tutorial or documenting your code, our syntax highlighting provides excellent support. You can use \inlinecode{inline code} for small snippets. For larger blocks:

\begin{lstlisting}[language=Python, caption={A simple Python function}, label={lst:factorial}]
def factorial(n):
    """Calculate the factorial of a non-negative integer."""
    if n < 0:
        raise ValueError("Factorial is not defined for negative numbers")
    elif n == 0 or n == 1:
        return 1
    else:
        return n * factorial(n - 1)
        
# Example usage:
result = factorial(5)
print(f"The factorial of 5 is {result}")
\end{lstlisting}

\section{Seamless Mathematics}
The template provides excellent support for mathematical notation, both inline and in display environments.

Inline equations like $\sum_{i=1}^n x_i^2 = x_1^2 + \dots + x_n^2$ fit perfectly within your text. For more complex expressions, use the `align` environment:
\begin{align}
    f(x) &= (x - 1)^2 \\
    f'(x) &= 2(x - 1)
\end{align}

\begin{notetbox}
    Notice how mathematical expressions are rendered clearly in both inline and display forms. The consistent styling ensures your document remains professional and easy to read.
\end{notetbox}

\section{Professional Tables and Figures}
Present your data and diagrams with elegance.

\subsection{Tables}
Tables are styled using the \inlinecode{booktabs} package for a clean, professional look without vertical lines.

\begin{table}[h!]
    \centering
    \caption{Sample Experimental Results}
    \label{tab:results}
    \begin{tabular}{@{}lrr@{}}
        \toprule
        Metric    & Value     & Uncertainty \\
        \midrule
        Mean      & $0.12$    & $\pm 0.03$  \\
        Std. Dev. & $1.05$    & $\pm 0.02$  \\
        Skewness  & $0.05$    & $\pm 0.01$  \\
        \bottomrule
    \end{tabular}
\end{table}

\subsection{Figures and Diagrams}
The template includes full support for TikZ, allowing you to create stunning, customised diagrams.

\begin{figure}[h!]
    \centering
    \begin{tikzpicture}[node distance=2.5cm, auto, >=Latex]
        % Define styles
        \tikzstyle{block} = [rectangle, draw, fill=maincolor!20,
                               text width=7em, text centered, rounded corners, minimum height=3em,
                               drop shadow={opacity=0.7, fill=black!50}]
        \tikzstyle{line} = [draw, -{Stealth[length=2mm, width=1.5mm]}, thick, color=accentcolor]

        % Place nodes
        \node [block] (init) {Initialise};
        \node [block, right=of init] (process) {Process Data};
        \node [block, right=of process] (output) {Output Results};

        % Draw edges
        \path [line] (init) -- (process);
        \path [line] (process) -- (output);
        \path [line, bend left=45] (output) edge node[above, midway, font=\tiny] {Feedback Loop} (init);
    \end{tikzpicture}
    \caption{A styled TikZ diagram showing a simple workflow with a feedback loop.}
    \label{fig:tikzflow}
\end{figure}

\section{Citations and Bibliography}
The template uses BibLaTeX for easy and powerful reference management. You can cite sources from your bibliography, such as \cite{Smith2020} or \cite{Lamport1994}.

\begin{notetbox}
    To use citations, ensure you have the \inlinecode{biber} bibliography processor installed and run the full compilation with \inlinecode{./compile.sh}.
\end{notetbox}

Simply add your references to the \inlinecode{references.bib} file. Here is an example entry:
\begin{lstlisting}[language=TeX, caption={Example reference entry in references.bib}, label={lst:reference}]
@article{Smith2020,
  author  = {Smith, John and Johnson, Sarah},
  title   = {Recent Advances in Document Preparation Systems},
  journal = {Journal of Documentation},
  year    = {2020},
  volume  = {76},
  number  = {3},
  pages   = {710--725},
  doi     = {10.1000/example.doi}
}
\end{lstlisting}

% Chapter 4: Theming Deep Dive
\chapter{Theming: Your Document, Your Style}
\label{chap:theming}
The powerful theming system is one of the standout features of this template. You can effortlessly change the entire look and feel of your document with a single command.

\section{One-Step Theme Switching}
To change your theme, simply edit the \inlinecode{\\usetheme} command at the top of this file. It takes two arguments: the font theme and the colour theme.
\begin{lstlisting}[language=TeX, caption={Using the theme switcher command}, label={lst:themeswitcher}]
% The first parameter is the font theme, the second is the colour theme.
\usetheme{font-theme}{colour-theme}

% Example: Modern fonts with the Oxford Blue theme
\usetheme{modern}{oxford-blue}

% Example: Elegant fonts with the Vintage Rose theme
\usetheme{elegant}{vintage-rose}
\end{lstlisting}

\section{Available Font Themes}
We have curated seven professional font pairings to suit any document. Your current theme is \textbf{\textcolor{accentcolor}{\fonttheme}}.
\begin{itemize}
    \item \textbf{\showcasemodern{modern}}: A contemporary look with Charter and Bera Sans (the default).
    \item \textbf{\showcaseclassic{classic}}: A traditional academic style with Palatino and TeX Gyre Heros.
    \item \textbf{\showcaseelegant{elegant}}: A refined style with EB Garamond and Source Sans Pro.
    \item \textbf{\showcaseacademic{academic}}: The cohesive Libertinus family, perfect for scholarly papers.
    \item \textbf{\showcasescientific{scientific}}: STIX Two and Cabin, optimised for scientific and mathematical content.
    \item \textbf{\showcaseprofessional{professional}}: An enhanced Palatino clone with Source Sans Pro for a smart, business look.
    \item \textbf{\showcasecontemporary{contemporary}}: Modern Fira Sans with matching mathematics support for a clean, unified feel.
\end{itemize}

\section{Available Colour Themes}
Choose from over 17 carefully designed colour themes.
\begin{itemize}
    \item \textbf{Cambridge Family}: \textbf{\textcolor{showcasecambridgeblue}{cambridge-blue}} (default), \textbf{\textcolor{showcasecambridgeclassic}{cambridge-classic}}, \textbf{\textcolor{showcasecambridgeforest}{cambridge-forest}}, \textbf{\textcolor{showcasecambridgesunset}{cambridge-sunset}}, \textbf{\textcolor{showcasecambridgeriver}{cambridge-river}}
    \item \textbf{Oxford Family}: \textbf{\textcolor{showcaseoxfordblue}{oxford-blue}}, \textbf{\textcolor{showcaseoxfordmist}{oxford-mist}}, \textbf{\textcolor{showcaseoxfordmonochrome}{oxford-monochrome}}
    \item \textbf{Sky Family}: \textbf{\textcolor{showcasesummerskies}{summer-skies}}, \textbf{\textcolor{showcaseauroraskies}{aurora-skies}}, \textbf{\textcolor{showcasetwilightskies}{twilight-skies}}, \textbf{\textcolor{showcasemidnightskies}{midnight-skies}}
    \item \textbf{Other Themes}: \textbf{\textcolor{showcasevintagerose}{vintage-rose}}, \textbf{\textcolor{showcaseemerald}{emerald}}, \textbf{\textcolor{showcaseroyalpurple}{royal-purple}}, \textbf{\textcolor{showcasearctic}{arctic}}, \textbf{\textcolor{showcaseautumn}{autumn}}
\end{itemize}

\section{Creating Your Own Colour Theme}
Feeling creative? You can easily define your own colour theme in \inlinecode{config/colours.tex}.

\begin{notetbox}
    To add your own theme, find the "CUSTOM THEME" section in \inlinecode{config/colours.tex} and follow the template pattern provided.
    \begin{itemize}
        \item Choose a unique theme name (e.g., \inlinecode{my-awesome-theme}).
        \item Define all the required colours.
        \item Activate it with \inlinecode{\\usetheme\{font-theme\}\{my-awesome-theme\}}.
    \end{itemize}
\end{notetbox}

Here is an example of what a custom theme definition looks like:
\begin{lstlisting}[language=TeX, caption={Custom theme definition in config/colours.tex}, label={lst:customtheme}]
% Add this block to config/colours.tex
\ifdefstring{\activetheme}{my-custom-theme}{%
    \definecolor{maincolor}{RGB}{76,40,130}       % Royal Purple
    \definecolor{accentcolor}{RGB}{212,175,55}    % Gold
    \definecolor{highlightcolor}{RGB}{220,20,60}  % Crimson
    \definecolor{codebg}{RGB}{245,240,255}        % Light purple background
    \definecolor{codefg}{RGB}{50,30,80}           % Dark purple foreground
    \definecolor{softgray}{RGB}{200,190,210}      % Purple-tinted grey
    \definecolor{titlepagebg}{RGB}{240,235,250}   % Soft purple background
    \definecolor{inlinecodebg}{RGB}{235,230,250}  % Richer purple for inline code
    \definecolor{inlinecodefg}{RGB}{90,50,150}    % Deeper royal purple for inline code
}{}

% Then, in elegant-notebook.tex:
\usetheme{modern}{my-custom-theme}
\end{lstlisting}

% Chapter 5: Advanced Customisation
\chapter{Advanced Customisation}
For those who want to dig deeper, the template offers even more ways to tailor your document.

\section{Creating Custom Box Types}
You can design your own box styles in \inlinecode{config/settings.tex}. For example, you could create a `warningbox` for critical alerts.
\begin{lstlisting}[language=TeX, caption={Creating a custom box type in config/settings.tex}, label={lst:custombox}]
\newtcolorbox{warningbox}{
    enhanced,
    colback=red!10,
    colframe=red!80!black,
    fonttitle=\sffamily\bfseries,
    coltitle=white,
    title=Warning,
    left=2mm, right=2mm, top=2mm, bottom=2mm,
    arc=2mm,
    drop shadow,
    breakable
}
\end{lstlisting}

\section{Understanding the Project Structure}
The template is organised into a clear and logical file structure, making it easy to find what you need.
\begin{lstlisting}[language=bash, caption={Project directory structure}, label={lst:structure}]
elegant-notebook.tex    # Main document (this file)
references.bib          # Bibliography file
README.md               # Project documentation
compile.sh              # Full compilation script
simple-compile.sh       # Basic compilation script
test-themes.tex         # Theme preview tool
config/                 # Configuration files
    colours.tex         # Colour theme definitions
    metadata.tex        # Document metadata (titles, author, etc.)
    settings.tex        # Core package imports and style settings
    theme.tex           # The theme switching system
    title-page.tex      # The title page layout
\end{lstlisting}

% Chapter 6: Conclusion and Best Practices
\chapter{Conclusion and Best Practices}
We hope you enjoy using the Elegant Notebook template. It is designed to be a powerful yet flexible tool that gets out of your way, so you can focus on what matters most: your content.

\begin{notetbox}[Best Practices for Best Results]
Here are a few final tips for getting the best results:
\begin{itemize}
    \item Keep your document organised with a clear hierarchy of chapters and sections.
    \item Use the provided environments (`notetbox', `exampletbox', etc.) consistently for visual coherence.
    \item Choose a font and colour theme that matches the tone and subject matter of your work.
    \item Always use the \inlinecode{./compile.sh} script for the final version to ensure all references and links are correct.
    \item For collaborative projects, we highly recommend using a version control system like Git.
\end{itemize}
\end{notetbox}

Happy writing!

% Section: References
\chapter*{References}
\printbibliography[heading=none]

\end{document} 